Case Study: ChIP-seq Differential Peak Calling (csaw)

### 2018-03-08 datasets/ChIP-seq/ChIPseq-csaw.Rmd
Fix typo in var name for counting

    ## filter windows by abundance
    bins <- windowCounts(meta$file, bin = TRUE, width = 2000, param = param)
    filter_stat <- filterWindows(win_cnts, bins, type = "global")
    keep <- filter_stat$filter > log2(3)
    filtered_cnts <- win_cnts[keep, ]

>>>>

    ## filter windows by abundance
    bins <- windowCounts(meta$sorted, bin = TRUE, width = 2000, param = param)
    filter_stat <- filterWindows(win_cnts, bins, type = "global")
    keep <- filter_stat$filter > log2(3)
    filtered_cnts <- win_cnts[keep, ]
